Download data

### 2024-05-15 scripts/subsetDataforCrews.Rmd
writing

p <- '/media/steppe/hdd/EmpiricalSeedZones/data/geodata/rasters'
f <- file.path(p, list.files(p, pattern = 'tif$'))
eSTZs <- rast(f)
names(eSTZs) <- gsub('-.*tif$', '', basename(f))
eSTZs <- project(eSTZs, 'epsg:5070') 
eSTZs <- resample(eSTZs, example_rast)
rm(f, p)

@@

plot(eSTZs)

>>>>

p <- '/media/steppe/hdd/EmpiricalSeedZones/data/geodata/rasters'
f <- file.path(p, list.files(p, pattern = 'tif$'))
eSTZs <- rast(f)
names(eSTZs) <- gsub('-.*tif$', '', basename(f))
eSTZs <- resample(eSTZs, example_rast, method = 'near')
rm(f, p)

@@
